Vragenlijst thesis evaluatie

### 2015-02-13 doc/template/chap-3.tex
commit

\section{Literatuurstudie}
\begin{description}
\item Distributed Worm Simulation with a REalistic Internet 2005  \\
Modeling of congestions of network through worm propagation. Mathematical model focussing on the underlying network infrastructure.(diff no game theory) 
\item Of threats and Costs: A Game-theoretic approach to security risk managment 2013\\
Model network security of networks with a non-cooperative node through game theory. Attacker knows the defense strategies and the defender has knowledge of the possible attacks. Each actor considers the actions of the other before deciding to strive to optimize their own utility. (diff not stealthy)
\item Game theory meet network security and privacy (2013) \\
Chapter 3 addresses several games in game theory for modeling network security.
\item Game theoretic approach for cost-benefit analysis of malware proliferation prevention (..)
Introduces SIS and SIR together with 'patch', 'removal' and 'patch and removal'.
\end{description}

>>>>

\section{Gametheory}

Game theory is the study between selfinterested agents and the actions they perform. self interested agents means not that they want to harm eachother or that they only care about themselfes. Agent has a description of the world he likes. A utility function is a mapping of the world that the agent likes to real numbers.

\section{Literatuurstudie}

Difference with FlipThem: subpart of nodes for control and strategy difference: dependant of grade of the nodes, instead of just periodic.
- Literatuurstudie
- Flipit
- Game Motivation
- Formal definition

\begin{description}
\item Distributed Worm Simulation with a Realistic Internet 2005  \\
Modeling of congestions of network through worm propagation. Mathematical model focussing on the underlying network infrastructure.(diff no game theory) 
\item Of threats and Costs: A Game-theoretic approach to security risk managment 2013\\
Model network security of networks with a non-cooperative node through game theory. Attacker knows the defense strategies and the defender has knowledge of the possible attacks. Each actor considers the actions of the other before deciding to strive to optimize their own utility. (diff not stealthy)
\item Game theory meet network security and privacy (2013) \\
Chapter 3 addresses several games in game theory for modeling network security.
\item Game theoretic approach for cost-benefit analysis of malware proliferation prevention (..)
Introduces SIS and SIR together with 'patch', 'removal' and 'patch and removal'.
\end{description}
